---
title: "Regression and Statistical Inference"
author: "Annmary Jose"
---
# Assignment 

1.  Read the data and check the dimensions. How many rows and how many columns does the data have?

```{r}

# Read data set.
df <- readRDS("../../Causal_Data_Science_Data/car_prices.rds")
dimension <- dim(df)
cat(" Number of rows:", dimension[1], "\n","Number of columns:", dimension[2], "\n")
```

2.  Use appropriate commands to get a more detailed look at the data. What data types do you see? How do numbers differ from strings regarding their data type?

    ```{r}

    library(tidyverse)

    install.packages("dplyr")
    library(dplyr)

    head(df)
    # Get glimpse of data
    glimpse(df)
    summary(df)

    ```

3.  Run a linear regression. You want to explain what factors are relevant for the pricing of a car.

    ```{r}

    l_r <- lm(price ~ .,data = df)
    summary(l_r)

    ```

4.  Choose one regressor and

    1.  explain what data type it is and what values it can take on

    2.  what effect is has on the price and what changing the value would have as a result

    3.  whether its effect is statistically significant.

```{r}
# Run a linear regression with mileage as a predictor for price
model <- lm(price ~ enginesize, data = df)

# Print the summary of the regression model
summary(model)

# 1. Data Type and Values
 data_type= class(df$enginesize)

```

1.  Data Type and Values

    Regressor choosed was enginesize whose data type is numeric and it takes numeric values

2.  Effect on Price

    The coefficient for enginesize is 170.064 and it has a poitive effect on price. when enginesize increases price also increases

3.  Statistical Significance

    The p-value associated with the enginesize coefficient \<2e-16. This extremely small p-value indicating that the enginesize coefficient is statistically significant.

5.  Add a variable `seat_heating` to the data and assign a value `TRUE` for all observations.

    ```{r}
    car_data_new <- df %>% 
      mutate(seat_heating = TRUE)


    # Run a regression with the new variable
    model_with_seat_heating <- lm(price ~  seat_heating, data = car_data_new)

    # Print the summary of the regression model
    summary(model_with_seat_heating)
    ```

The coefficient with seat heating is NA
