---
title: "Directed Acyclic Graphs"
author: "Annmary Jose"
---

# Assignment

1.  Draw the DAG for parking slot

```{r}
#install and load necessary package
library("tidyverse")
#install.packages("dagitty")
#install.packages("ggdag")
library(dagitty)
library(ggdag)

```

```{r}

# with confounder
dag <- dagify(
  parkingslot ~ location,
  sales ~ location,
  sales ~ parkingslot,
  coords = list(x = c(parkingslot = 1, sales = 3, location = 2),
                y = c(parkingslot = 1, sales = 1, location = 2)),
  labels = c("ParkingSpots" = "A")
)

# Plot DAG
ggdag(dag, text = F) +
  geom_dag_point(color = "green")+
  geom_dag_text(color = NA) +
  geom_dag_edges(edge_color = "yellow") +
  geom_dag_label_repel(aes(label = name))
```

2.  Load the data file `customer_sat.rds`.

    ```{r}
    data <- readRDS("../../Causal_Data_Science_Data/customer_sat.rds")
    view(data)
    ```

    1.  regress `satisfaction` on `follow_ups`

    ```{r}
    regression_1 <- lm(satisfaction ~ follow_ups, data = data)

    summary(regression_1)
    ```

```{=html}
<!-- -->
```
2.  regress `satisfaction` on `follow_ups` and account for `subscription`

    ```{r}

    regression_2 <- lm(satisfaction ~ follow_ups + subscription, data = data)

    summary(regression_2)


    ```

3.   Compare the coefficients and find a possible explanation.

-   In the first regression,the coefficient for follow_ups is negative( -3.3093). This implies that for each additional follow-up, satisfaction decreases by 3.3093 units.

-   In the second regression,the coefficient for follow_ups is now positive (2.1944), suggesting that, on average, satisfaction increases by 2.1944 units for each additional follow-up.

4.  Plot the data. 

```{r}

not_cond <- ggplot(data, aes(x = satisfaction, y = follow_ups)) +
  geom_point(alpha =0.8) +
  stat_smooth(method = "lm", se = F)

  
cond <- ggplot(data, aes(x = satisfaction, y = follow_ups,
                            color = subscription)) +
  geom_point(alpha =0.8) +
  stat_smooth(method = "lm", se = F) +
  theme(legend.position = "right")

# Plot both
not_cond
cond
```
