---
title: "Instrumental Variables"
author: "Annmary Jose"
---

# Assignment 

Load necessary library and data set

```{r}
library(tidyverse)
library(dplyr)
library(ggdag)
library(dagitty)

data <- readRDS("../../Causal_Data_Science_Data/rand_enc.rds")
data
```

1.  Draw a Dag

```{r}

dag <- dagify(
  used_ftr ~ rand_enc,
  time_spent ~ used_ftr,
  coords = list(x = c(rand_enc = 1, used_ftr = 2, time_spent = 3),
                y = c(rand_enc = 1, used_ftr = 1, time_spent = 1))
)

# Plot DAG
ggdag(dag, text = F) +
  geom_dag_point(color = "blue")+
  geom_dag_text(color = NA) +
  geom_dag_edges(edge_color = "black") +
  geom_dag_label_repel(aes(label = name))
```

2.  Compute the naive, biased estimate.

```{r}

model_biased <- lm(time_spent ~ used_ftr, data = data)
summary(model_biased)

model_naive <- lm(rand_enc ~ used_ftr, data = data)
summary(model_naive)

```

-   **Model 1**: When the new feature is used, the model estimates an increase of approximately 10.82 units in the time spent on the app, compared to when the feature is not used.

-   **Model 2**: When the new feature is used, the model estimates an increase in the probability of being encouraged by approximately 0.21.

    2.  Argue whether instrumental variable estimation is an adequate procedure.

```{r}

cor(data$rand_enc, data$used_ftr)
```

The positive correlation between **`rand_enc`** and **`used_ftr`** suggests relevance, a key assumption for instrumental variable estimation.

4.  Compute the IV estimate using 2SLS and compare it to the naive estimate

```{r}

library(estimatr)
model_iv <- iv_robust(time_spent ~ used_ftr | rand_enc, data = data)
summary(model_iv)

```
